A 38 Million Year Old Mini-Neptune in the Kepler Field

### 2021-10-10 paper/ms.tex
update ms
revised TTV analysis

% 208 words (250 max)
\begin{abstract}
  Kepler\,1627A is a G8V star previously known to host a
  $3.8\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  The star was
  observed by the Kepler space telescope because it is nearby
  ($d=329\,{\rm pc}$) and it resembles the Sun.  Here we show using
  Gaia kinematics, TESS stellar rotation periods, and spectroscopic
  lithium abundances that Kepler\,1627 is a member of the \clusterage\
  old $\delta$~Lyr cluster.  To our knowledge, this makes
  Kepler\,1627Ab the youngest planet with a precise age yet found by
  the main Kepler mission.  The Kepler photometry shows two
  peculiarities: the average transit profile is asymmetric, and the
  individual transit times are correlated with the local light curve
  slope.  We discuss possible explanations for each anomaly.  More
  broadly, the $\delta$~Lyr cluster
  is one of $\sim$10$^3$ coeval groups whose properties have been clarified
  by Gaia.  Many other exoplanet hosts are potentially kinematic members
  of these clusters; their candidate memberships can be verified by
  measuring stellar rotation periods in the TESS full frame images.
\end{abstract}

@@

Matching our young star list against stars observed by Kepler revealed
that Kepler observed a portion of the \cn\ (Stephenson-1; Theia~73).
More specifically, a clustering analysis of the Gaia data by
\citet{KounkelCovey2019} reported that Kepler~1627 (KIC 6184894; KOI
5245; TIC 120105470) is a \cn\ member.  Given the previous statistical
validation of the close-in mini-Neptune Kepler 1627b
\citep{2012ApJS..199...24T,morton_false_2016,thompson_planetary_2018},
we begin by examining the properties of the cluster
(Section~\ref{sec:cluster}).  We find that the $\delta$ Lyr cluster is
\clusterage\ old, and in Section~\ref{sec:stars} show that \sn\ is
both a binary and also a member of the cluster.  Focusing on the
planet (Section~\ref{sec:planet}), we confirm that despite the
existence of the previously unreported M2.5V companion, hereafter
Kepler\,1627B, the planet orbits the G-dwarf primary, Kepler\,1627A.
Based on a correlation between the planetary transit times and the
local light curve slope, the orbit may also be prograde.  We conclude
by highlighting broader implications for our ability to age-date a
larger sample of planets (Section~\ref{sec:conc}).

@@

We fitted the Kepler long cadence time series with a model that
simultaneously included the planetary transit and the stellar
variability.  The stellar variability was modeled with the
\texttt{RotationTerm} Gaussian Process kernel in \texttt{exoplanet}
\citep{exoplanet:exoplanet}.  This kernel assumes that the variability
is generated by a mixture of two damped simple harmonic oscillators
with characteristic frequencies set by 1/$P_{\rm rot}$ and its first
harmonic.  We additionally included a jitter term to inflate the flux
uncertainties in a manner that accounted for otherwise unmodeled
excess white noise, and let the eccentricity float.  For the
limb-darkening, we assumed a quadratic law, and sampled using the
uninformative prior suggested by \citet{exoplanet:kipping13}.

@@

The transit fit however is not perfect: the lower panels of
Figure~\ref{fig:lc} show an asymmetric residual in the data relative
to the model: the measured flux is high during the first half of
transit, and low in the second half.  The semi-amplitude of this
deviation is $\approx50\,{\rm ppm}$, which represents a $\approx 3\%$
distortion of the transit depth ($1759\pm62\,{\rm ppm}$).  Note that
while this asymmetry is within the 2-$\sigma$ model uncertainties, the
model has a jitter term that grows to account for otherwise unmodeled
white noise in the flux.  The significance of the asymmetry is
therefore best assessed in comparison against the intrinsic
out-of-transit scatter in the data, not the model uncertainties.

To determine whether the asymmetry is a systematic caused by our
stellar variability model, we explored an alternative approach in
which we isolated each transit window and locally fitted out
polynomial trends, and then binned all the observed transits; the
asymmetry was still present at a comparable amplitude.
Appendix~\ref{app:asymmetry} includes a deeper analysis, and finds
that the asymmetry also seems to be robust to different methods of
data binning in time and by local light curve slope.  Possible
astrophysical explanations are discussed in Section~\ref{sec:conc}.

@@

\begin{figure}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.49\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf Evidence for a prograde orbit of Kepler 1627 Ab.} The time of
    each Kepler transit was measured, along with the local slope of
    the light curve.  The two quantities appear anti-correlated, which
    could be explained by starspot crossings during the first
    (second) half of transit inducing a positive (negative) TTV,
    provided that the orbit is prograde \citep{mazeh_time_2015}.  The
    units along the abscissa can be understood by considering that the
    stellar flux changes by $\sim$60\,ppt per half rotation period
    ($\sim$1.3\,days).
		\label{fig:corr}
	}
\end{figure}

@@

There are two other new lines of evidence that confirm the planetary
interpretation.  First, the stellar density implied by the transit duration and orbital period
is inconsistent with an eclipsing body around the M-dwarf companion:
we find $\rho_\star = 2.00 \pm 0.24\,{\rm g\,cm}^{-3}$, while the
theoretically expected density for Kepler\,1627B is $\approx 4.6\,{\rm
g\,cm}^{-3}$ (Table~\ref{tab:posterior}; \citealt{choi_mesa_2016}).
The transit duration is therefore too long to be explained by a star
eclipsing the M dwarf secondary at $10$-$\sigma$.  While the planet
might hypothetically still orbit a hidden close and bright companion,
this possibility is implausible given {\it i)} the lack of secondary lines in
the HIRES spectra and {\it ii)} the lack of secondary rotation signals
in the Kepler photometry.

@@

The second line of confirming evidence comes by analyzing the
individual Kepler transit times. We isolated each of the 144 observed
transits to within $\pm4.5$\,hr of each transit, and fitted each
window with both {\it i)} a local second-order polynomial and transit,
and {\it ii)} a local linear trend.  We let the mid-time of each
transit float, and then calculated the residual between the measured
mid-time and that of a periodic orbit.  This residual, the transit
timing variation (TTV), is plotted in Figure~\ref{fig:corr} against
the local linear slope.  A significant correlation of $-0.0564 \pm
0.0098\ {\rm ppt\,day}^{-1}$ is observed.  Fewer than ten Kepler
Objects of Interest have shown this correlation
\citep{holczer_time_2015}, which can be explained as a TTV
induced by unresolved starspot crossings \citep{mazeh_time_2015}.
This is only possible if the planet transits the primary star, which
excludes a background eclipsing binary scenario, and therefore
confirms that \pn\ is a planet.  It also suggests that the planet's
orbit is prograde.  The latter point assumes that the dominant
photometric variability is induced by dark spots, and not bright
faculae.  Given the observed transition of Sun-like stellar
variability from spot to faculae-dominated regimes between young and
old ages, we expect this assumption to be reasonably secure
\citep{shapiro_are_2016,montet_long-term_2017,reinhold_stellar_2020}.

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{f7.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Keck/HIRES radial velocities and MuSCAT3 photometry from the transit of 2021 Aug 7.}
    {\it Top:} 
    The radial velocity jitter across the 15~minute exposures
    ($\sigma_{\rm RV}\approx30$\ms) prevented us from detecting the RM
    effect;
    a model including the RM anomaly and a quadratic trend in time to
    fit the spot-induced $\approx$\,$250$\ms\ trend is shown (see
    Appendix~\ref{app:rm}).  Shaded bands show 2-$\sigma$ model
    uncertainties.  
    {\it Middle:} The RV variations are strongly correlated with varying
    emission in the Ca H and K lines.
    {\it Bottom}: The photometric transit depths are consistent across
    the {\it griz} bandpasses. The photometry is binned at 10~minute
    intervals.
		\label{fig:ground}
	}
\end{figure}

A third supporting line of evidence for the planetary interpretation
exists, though we consider it less definitive than the stellar density
and TTV-local slope correlation.  We observed a transit of \pn\ on the
night of 2021 Aug 7 simultaneously with Keck/HIRES and MuSCAT3.  We
scheduled the observations using the ephemeris of
\citet{holczer_transit_2016}.  Although we did not detect the
Rossiter-McLaughlin (RM) anomaly, the multi-band MuSCAT3 light curves
show the transit (Figure~\ref{fig:ground}).  Fitting the MuSCAT3
photometry with a model that lets the transit depths vary across each
bandpass, we find {\it griz} depths consistent with the Kepler depth
at 0.6, 0.3, 0.3, and 1.1-$\sigma$ respectively.  Conditioned on the
Kepler ephemeris and transit depth, the MuSCAT3 observations may also
suggest a transit duration $17.3\pm4.3\ {\rm minutes}$ shorter than the
Kepler transits; further photometric follow-up could help confirm
whether the transit duration is indeed changing.  For our RM analysis,
the details are discussed in Appendix~\ref{app:rm}.  While the
velocities are marginally more consistent with a prograde or polar
orbit than a retrograde orbit, the spot-corrected exposure-to-exposure
scatter ($\sigma_{\rm RV}\approx 30$\ms) is comparable to the expected
RM anomaly assuming an aligned orbit ($\Delta v_{\rm RM}\approx
20\,{\rm m\,s}^{-1}$).  We are therefore not in a position to claim a
spectroscopic detection of the RM effect, nor to quantify the stellar
obliquity.

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.8\textwidth]{f8.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Radii, orbital periods, and ages of transiting exoplanets}.
    Planets younger than a gigayear with ${\rm \tau}/\sigma_{\tau} >
    3$ are emphasized, where $\tau$ is the age and $\sigma_{\tau}$ is
    its uncertainty.  \pn\ is shown with a star.  The large sizes of
    the youngest transiting planets could be explained by their
    primordial atmospheres not yet having evaporated; direct
    measurements of the atmospheric outflows or planetary masses would
    help to confirm this expectation.  Selection effects may also be
    important.  Parameters are from the NASA Exoplanet Archive (2021
    Sept 15).
		\label{fig:rp_period_age}
	}
\end{figure*}

@@

More immediately, the Kepler data may yet contain additional
information.  For instance, one possible explanation for the transit
asymmetry shown in Figure~\ref{fig:lc} is that of a dusty asymmetric
outflow.  A second possibility is that the planetary orbit is slightly
misaligned from the stellar spin axis, and tends to transit starspot
groups at favored stellar latitudes.  Other possibilities such as
gravity darkening or TTVs causing the asymmetry are disfavored (see
Appendix~\ref{app:asymmetry}).  Dusty outflows are theoretically
expected for young mini-Neptunes, and the amplitude of the observed
asymmetry is also consistent with predictions \citep{wang_dai_2019}.
Beyond the asymmetric transits, Appendix~\ref{app:flare} highlights an
additional abnormality in the Kepler data, in the arrival time
distribution of stellar flares.  We encourage its exploration by
investigators more versed in the topic than ourselves.

@@

\begin{figure}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f11.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Transit models and residuals, binned by quartiles in the
    local slope of the light curve}.  
    Representative uncertainties for the black points (binned at 20
    minute intervals) are shown in the lower right of each panel.  A
    similar transit asymmetry to that shown in Figure~\ref{fig:lc}
    seems to be present in three of the four bins.
    \vspace{-0.5cm}
		\label{fig:phaseslope}
	}
\end{figure}
\begin{figure}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f12.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Transit models and residuals, binned by quartiles of transit
    timing variations}.  The data are otherwise the same as in
    Figure~\ref{fig:phaseslope}.
		\label{fig:phasettv}
	}
\end{figure}

@@

As a means of exploring the robustness of the transit asymmetry,
Figures~\ref{fig:phasequarter},~\ref{fig:phaseyear},~\ref{fig:phaseslope},
and~\ref{fig:phasettv} show the Kepler data binned in four ways: over
Kepler quarters, Julian years, quartiles of local slope, and quartiles
of transit timing variation.  Over Kepler quarters
(Figure~\ref{fig:phasequarter}), Quarter 6 shows the strongest
asymmetry: a deviation of about 3\,ppt from expectation.  Quarter 7
shows an anomaly at roughly the same transit phase.  Year 2
correspondingly shows the strongest anomaly out of any year in
Figure~\ref{fig:phaseyear}; the asymmetry is visually apparent however
in each of Years 2, 3, and 4.

To bin by quartiles in local slope and TTV, we used our measurements
of the local linear slopes in each of the observed transit windows
(144 transits total).  Four outlier transits were removed, leaving 140
transits.  These were then divided into quartiles, so that each panel
shows 35 transits binned together.  The exact light curve slope and
TTV intervals are listed in the lower left panels of
Figures~\ref{fig:phaseslope} and~\ref{fig:phasettv}.  Binned by local
slope quartiles (Figure~\ref{fig:phaseslope}), the asymmetry is
visually present in three of the four quartiles: the only bin in which
it does not appear is ${\rm d}f/{\rm d}t\in[0.001,0.033]\,{\rm
ppt\,day}^{-1}$.  The corresponding bins in TTV (largest TTV
corresponding to smallest ${\rm d}f/{\rm d}t$) show the same
asymmetries, though with somewhat greater scatter
(Figure~\ref{fig:phasettv}).

Within the theory presented by \citet{mazeh_time_2015}, unresolved
starspot crossings cause the correlation between TTVs and the local
light curve slope (Figure~\ref{fig:corr}).  In this model, we would
expect the light curves with the most negative local slopes to have
the largest positive TTVs, due to spot crossing events during the
latter half of transit.  The lower-right panel of
Figure~\ref{fig:phasettv} and upper-left panel of
Figure~\ref{fig:phaseslope} agree with this expectation.  However, we
would also expect the sign of the effect to reverse when considering
the most positive local slopes, and the most negative TTVs.  The
upper-left panel of Figure~\ref{fig:phasettv} and lower-right panel of
Figure~\ref{fig:phaseslope} contradict this expectation: the residual
in both cases maintains the same parity!  On the one hand, this shows
that the residual is not dependent on the local light curve slope,
which mitigates the possibility that it might be an artifact of our
detrending methods.  On the other, it raises the question of whether
unresolved starspot crossings are indeed the root cause of the
correlation shown in Figure~\ref{fig:corr}.

% FIXME: KM to discuss injection recovery...

@@

The transit asymmetry seems robust against most methods of binning the
data, though with some caveats ({\it e.g.}, the ``middle quartile'' in
local flux (${\rm d}f/{\rm d}t\in[0.001,0.033]\,{\rm ppt\,day}^{-1}$),
where the asymmetry does not appear).  Nonetheless, if the effect were
entirely systematic we would expect to see it change as a function of
the sign of the local slope or TTV.  We therefore considered four
possible astrophysical interpretations: gravity darkening, transit
timing variations, spot-crossing events, and a persistent asymmetric
dusty outflow.

@@

The scenario of transit timing variations (TTVs) producing the
asymmetry seems unlikely because our analysis showed that transit
timing variations in \sn\ have amplitudes smaller than $\approx$10
minutes (see Figure~\ref{fig:corr}).  This is consistent with previous
results from \citet{holczer_transit_2016}.  Moreover, the transit
timing variations we do observe are correlated with the local light
curve slope, which on average increases as much as it decreases.  From
our analysis, the mean TTV and its standard deviation are
$0.00\pm12.05$ minutes; similarly the mean local slope and its
standard deviation are $0.49\pm44.49$\,ppt\,day$^{-1}$.  There is
therefore no expectation for TTVs to produce the asymmetry.  A
separate line of argument comes from Figure~\ref{fig:phaseslope}.  If
the local slope were essential to producing the transit asymmetry, we
would expect that in the largest ${\rm d}f/{\rm d}t$ bin, ${\rm
d}f/{\rm d}t\in[0.033,0.092]\,{\rm ppt\,day}^{-1}$, the sign of the
asymmetry would reverse.  We do not see evidence for this being the
case.

>>>>

% 208 words (250 max)
\begin{abstract}
  Kepler\,1627A is a G8V star previously known to host a
  $3.8\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  The star was
  observed by the Kepler space telescope because it is nearby
  ($d=329\,{\rm pc}$) and it resembles the Sun.  Here we show using
  Gaia kinematics, TESS stellar rotation periods, and spectroscopic
  lithium abundances that Kepler\,1627 is a member of the \clusterage\
  old $\delta$~Lyr cluster.  To our knowledge, this makes
  Kepler\,1627Ab the youngest planet with a precise age yet found by
  the main Kepler mission.  The Kepler photometry shows two
  peculiarities: the average transit profile is asymmetric, and the
  individual transit times might be correlated with the local light curve
  slope.  We discuss possible explanations for each anomaly.  More
  importantly, the $\delta$~Lyr cluster
  is one of $\sim$10$^3$ coeval groups whose properties have been clarified
  by Gaia.  Many other exoplanet hosts are potentially kinematic members
  of these clusters; their candidate memberships can be verified by
  measuring stellar rotation periods in the TESS full frame images.
\end{abstract}

@@

Matching our young star list against stars observed by Kepler revealed
that Kepler observed a portion of the \cn\ (Stephenson-1; Theia~73).
More specifically, a clustering analysis of the Gaia data by
\citet{KounkelCovey2019} reported that Kepler~1627 (KIC 6184894; KOI
5245; TIC 120105470) is a \cn\ member.  Given the previous statistical
validation of the close-in mini-Neptune Kepler 1627b
\citep{2012ApJS..199...24T,morton_false_2016,thompson_planetary_2018},
we begin by examining the properties of the cluster
(Section~\ref{sec:cluster}).  We find that the $\delta$ Lyr cluster is
\clusterage\ old, and in Section~\ref{sec:stars} show that \sn\ is
both a binary and also a member of the cluster.  Focusing on the
planet (Section~\ref{sec:planet}), we confirm that despite the
existence of the previously unreported M2.5V companion, hereafter
Kepler\,1627B, the planet orbits the G-dwarf primary, Kepler\,1627A.
We also analyze an asymmetry in the average transit profile, and a
possible correlation between the individual transit times and the
local light curve slope.  We conclude by discussing broader
implications for our ability to age-date a larger sample of planets
(Section~\ref{sec:conc}).

@@

\subsubsection{Transit and Stellar Variability Model}
We fitted the Kepler long cadence time series with a model that
simultaneously included the planetary transit and the stellar
variability.  The stellar variability was modeled with the
\texttt{RotationTerm} Gaussian Process kernel in \texttt{exoplanet}
\citep{exoplanet:exoplanet}.  This kernel assumes that the variability
is generated by a mixture of two damped simple harmonic oscillators
with characteristic frequencies set by 1/$P_{\rm rot}$ and its first
harmonic.  We additionally included a jitter term to inflate the flux
uncertainties in a manner that accounted for otherwise unmodeled
excess white noise, and let the eccentricity float.  For the
limb-darkening, we assumed a quadratic law, and sampled using the
uninformative prior suggested by \citet{exoplanet:kipping13}.

@@

\subsubsection{Transit Asymmetry}
\label{subsec:asymmetry}
The transit fit however is not perfect: the lower panels of
Figure~\ref{fig:lc} show an asymmetric residual in the data relative
to the model: the measured flux is high during the first half of
transit, and low in the second half.  The semi-amplitude of this
deviation is $\approx50\,{\rm ppm}$, which represents a $\approx 3\%$
distortion of the transit depth ($\delta=1759\pm62\,{\rm ppm}$).  Note that
although this asymmetry is within the 2-$\sigma$ model uncertainties, the
model has a jitter term that grows to account for otherwise unmodeled
white noise in the flux.  The significance of the asymmetry is
therefore best assessed in comparison against the intrinsic
out-of-transit scatter in the data ($\approx16\,{\rm ppm}$), not the model uncertainties.  The
lower right panel of Figure~\ref{fig:lc} demonstrates that the scatter during
transit is higher than during all other phases of the planet's orbit.

To determine whether the asymmetry could be a systematic caused by our
stellar variability model, we explored an alternative approach in
which we isolated each transit window, locally fitted out
polynomial trends, and then binned all the observed transits; the
asymmetry was still present at a comparable amplitude.
Appendix~\ref{app:asymmetry} describes a more detailed analysis, which finds
that the asymmetry also seems to be robust to different methods of
data binning in time and by local light curve slope.  Possible
astrophysical explanations are discussed in Section~\ref{sec:conc}.

\subsubsection{Transit Timing and the Local Slope}
\label{subsec:ttvslope}

\begin{figure}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.49\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf Possible evidence for a prograde orbit of Kepler 1627 Ab.} The time of
    each Kepler transit was measured, along with the local slope of
    the light curve.  The two quantities are weakly anti-correlated
    ($\approx$2-$\sigma$), which
    could be explained by starspot crossings during the first
    (second) half of transit inducing a positive (negative) TTV,
    provided that the orbit is prograde \citep{mazeh_time_2015}.  The
    units along the abscissa can be understood by considering that the
    stellar flux changes by $\sim$60\,ppt per half rotation period
    ($\sim$1.3\,days).
		\label{fig:corr}
	}
\end{figure}

The previous analysis by \citet{holczer_transit_2016} did not
find any significant long-term transit timing or duration variations
for \sn\ (TTVs or TDVs).  Quantitatively, the mean and standard deviation of the
TTVs and TDVs they measured were $-1.1\pm13.8\,{\rm
min}$ and $-3.3\pm22.1\,{\rm min}$.  In an
earlier analysis however, \citet{holczer_time_2015} studied correlations
between TTVs and local light curve slopes, and for \sn\
found a weak correlation of $-29\pm13\,{\rm min}\,{\rm day}^{-1}$
between the two quantities.  While this constitutes only weak
statistical evidence, given the possible connection between such
correlations and the unresolved starspot crossings that we expect to
be present in the data for \sn\ \citep{mazeh_time_2015}, we opted to re-examine the
individual transit times.

We therefore isolated each of the 144 observed transits to within
$\pm4.5$\,hr of each transit, and fitted each window with both {\it
i)} a local polynomial baseline plus the transit, and {\it ii)} a local linear
trend.  We considered the results both for a second and fourth-order
time-dependence in the local baseline.  We let the mid-time of each
transit float, and then calculated the residual between the measured
mid-time and that of a periodic orbit.  This residual, the transit
timing variation, is plotted in Figure~\ref{fig:corr} against
the local linear slope for the fourth-order polynomial baseline.  The
slope of $-21 \pm 10\,{\rm min\,day}^{-1}$ is similar to that
found by \citet{holczer_time_2015}.

One concern we had in this analysis was whether our transit fitting
procedure might induce spurious correlations between the slope and
transit time.  In particular, using the second-order polynomial
baseline yielded a larger anti-correlation between the TTVs and local
slopes, of $-79 \pm 14\,{\rm min\,day}^{-1}$.  We therefore
performed an injection-recovery procedure in which we injected
transits at different phases in the \sn\ light curve and repeated the
TTV analysis.  This was done at $\approx$50 phases, each separated by
$0.02\,P_{\rm orb}$ while omitting the phases in transit.  For
the second-order polynomial baseline, this procedure yielded
similar anti-correlations in the injected transits to that present in the real
transit;
using this baseline would therefore bias the
result.  However for the fourth-order baseline, the correlation
present in the data was stronger than in all but one of the injected
transits.
Possible interpretations are discussed below, however given the
statistical significance, this analysis should be interpreted as
suggestive at best.

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.45\textwidth]{f7.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Keck/HIRES radial velocities and MuSCAT3 photometry from the transit of 2021 Aug 7.}
		{\it Top:} 
		The radial velocity jitter across the 15~minute exposures
		($\sigma_{\rm RV}\approx30$\ms) prevented us from detecting the RM
		effect;
		a model including the RM anomaly and a quadratic trend in time to
		fit the spot-induced $\approx$\,$250$\ms\ trend is shown (see
		Appendix~\ref{app:rm}).  Shaded bands show 2-$\sigma$ model
		uncertainties.  
		{\it Middle:} The RV variations are strongly correlated with varying
		emission in the Ca H and K lines.
		{\it Bottom}: The photometric transit depths are consistent across
		the {\it griz} bandpasses. The photometry is binned at 10~minute
		intervals.
		\label{fig:ground}
	}
\end{figure}

@@

Beyond this simple test, a line of evidence that
effectively confirms the planetary interpretation is that the stellar density
implied by the transit duration and orbital period is inconsistent
with an eclipsing body around the M-dwarf companion.  We find
$\rho_\star = 2.00 \pm 0.24\,{\rm g\,cm}^{-3}$, while the
theoretically expected density for Kepler\,1627B is $\approx 4.6\,{\rm
g\,cm}^{-3}$ (Table~\ref{tab:posterior}; \citealt{choi_mesa_2016}).
The transit duration is therefore too long to be explained by a star
eclipsing the M dwarf secondary at $10$-$\sigma$.  While the planet
might hypothetically still orbit a hidden close and bright companion,
this possibility is implausible given {\it i)} the lack of secondary
lines in the HIRES spectra and {\it ii)} the lack of secondary
rotation signals in the Kepler photometry.

@@

The correlation noted in Section~\ref{subsec:ttvslope} between the
TTVs and the local light curve slope could be a further line of evidence
in support of the planetary interpretation.  Unless it is a
statistical fluke (a $\approx$5\% possibility), then its most likely
cause is unresolved starspot
crossings \citep{mazeh_time_2015}.  This would only be possible if the
planet transits the primary star, which excludes a background
eclipsing binary scenario.  It would also suggest that the planet's
orbit is prograde.  The latter point assumes that the dominant
photometric variability is induced by dark spots, and not bright
faculae.  Given the observed transition of Sun-like stellar
variability from spot to faculae-dominated regimes between young and
old ages, we expect this latter assumption to be reasonably secure
\citep{shapiro_are_2016,montet_long-term_2017,reinhold_stellar_2020}.

A third supporting line of evidence for the planetary interpretation
also exists.  We observed a transit of \pn\ on the
night of 2021 Aug 7 simultaneously with Keck/HIRES and MuSCAT3.  We
scheduled the observations using the ephemeris of
\citet{holczer_transit_2016}.  Although we did not detect the
Rossiter-McLaughlin (RM) anomaly, the multi-band MuSCAT3 light curves
show that the transit is achromatic (Figure~\ref{fig:ground}).
Quantitatively, when we fitted the MuSCAT3
photometry with a model that lets the transit depths vary across each
bandpass, we found {\it griz} depths consistent with the Kepler depth
at 0.6, 0.3, 0.3, and 1.1-$\sigma$ respectively.  Conditioned on the
Kepler ephemeris and transit depth, the MuSCAT3 observations also
suggested a transit duration $17.3\pm4.3\ {\rm minutes}$ shorter than the
Kepler transits.
However, given both the lack of transit duration variations in the Kepler data
and the relatively low signal-to-noise of the MuSCAT3 transit,
further photometric follow-up would be necessary to determine
whether the transit duration is indeed changing.  
For our RM analysis,
the details are discussed in Appendix~\ref{app:rm}.  While the
velocities are marginally more consistent with a prograde or polar
orbit than a retrograde orbit, the spot-corrected exposure-to-exposure
scatter ($\sigma_{\rm RV}\approx 30$\ms) is comparable to the expected
RM anomaly assuming an aligned orbit ($\Delta v_{\rm RM}\approx
20\,{\rm m\,s}^{-1}$).  We are therefore not in a position to claim a
spectroscopic detection of the RM effect, nor to quantify the stellar
obliquity.

@@

\begin{figure}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f8.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Radii, orbital periods, and ages of transiting exoplanets}.
    Planets younger than a gigayear with ${\rm \tau}/\sigma_{\tau} >
    3$ are emphasized, where $\tau$ is the age and $\sigma_{\tau}$ is
    its uncertainty.  \pn\ is shown with a star.  The large sizes of
    the youngest transiting planets could be explained by their
    primordial atmospheres not yet having evaporated; direct
    measurements of the atmospheric outflows or planetary masses would
    help to confirm this expectation.  Selection effects may also be
    important.  Parameters are from the NASA Exoplanet Archive (2021
    Sept 15).
		\label{fig:rp_period_age}
	}
\end{figure}

@@

More immediately, the Kepler data may yet contain additional
information.  For instance, one possible explanation for the transit
asymmetry shown in Figure~\ref{fig:lc} is that of a dusty asymmetric
outflow.  
Dusty outflows are theoretically
expected for young mini-Neptunes, and the amplitude of the observed
asymmetry is also consistent with predictions \citep{wang_dai_2019}.
A second possibility is that the planetary orbit is slightly
misaligned from the stellar spin axis, and tends to transit starspot
groups at favored stellar latitudes.  
This somewhat contrived geometry would be necessary in order to
explain why the starspot crossings would add up coherently.
Other possible explanations such as
gravity darkening or TTVs causing the asymmetry are disfavored (see
Appendix~\ref{app:asymmetry}).  
Aside from the asymmetric transits, Appendix~\ref{app:flare}
highlights an additional abnormality in the short-cadence Kepler data, in the
arrival time distribution of stellar flares.  We encourage its
exploration by investigators more versed in the topic than ourselves.

@@

\begin{figure}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f11.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Transit models and residuals, binned by quartiles in the
    local slope of the light curve}.  
    Representative uncertainties for the black points (binned at 20
    minute intervals) are shown in the lower right of each panel.  A
    similar transit asymmetry to that shown in Figure~\ref{fig:lc}
    seems to be present in three of the four bins.
    \vspace{-0.5cm}
		\label{fig:phaseslope}
	}
\end{figure}

@@

As a means of exploring the robustness of the transit asymmetry,
Figures~\ref{fig:phasequarter},~\ref{fig:phaseyear}, and~\ref{fig:phaseslope}
show the Kepler data binned in three ways: over
Kepler quarters, Julian years, and quartiles of local slope.  Over Kepler quarters
(Figure~\ref{fig:phasequarter}), Quarter 6 shows the strongest
asymmetry: a deviation of about 3\,ppt from expectation.  Quarter 7
shows an anomaly at roughly the same transit phase.  Year 2
correspondingly shows the strongest anomaly out of any year in
Figure~\ref{fig:phaseyear}; the asymmetry is visually apparent however
in each of the four years.

To bin by quartiles in local slope, we used our measurements
of the local linear slopes in each of the observed transit windows
(144 transits total).  Four outlier transits were removed, leaving 140
transits.  These were then divided into quartiles, so that each panel
shows 35 transits binned together.  The exact light curve slope intervals are listed in the lower left panels of
Figure~\ref{fig:phaseslope}.  Binned by local
slope quartiles (Figure~\ref{fig:phaseslope}), the asymmetry is
visually present in three of the four quartiles: the only bin in which
it does not appear is ${\rm d}f/{\rm d}t\in[3.0,32.5]\,{\rm
ppt\,day}^{-1}$.

Within the theory presented by \citet{mazeh_time_2015}, unresolved
starspot crossings cause the weak correlation between TTVs and the local
light curve slope (Figure~\ref{fig:corr}).  In this model, we would
expect the light curves with the most negative local slopes to have
the largest positive TTVs, due to spot crossing events during the
latter half of transit.  The upper-left panel of
Figure~\ref{fig:phaseslope} agrees with this expectation.  However, we
would also expect the sign of the effect to reverse when considering
the most positive local slopes (most negative TTVs).  The
lower-right panel of
Figure~\ref{fig:phaseslope} contradicts this expectation: the residual
in both cases maintains the same parity!  On the one hand, this shows
that the residual is not dependent on the local light curve slope,
which lowers the likelihood that it might be an artifact of our
detrending methods.  On the other, it raises the question of whether
unresolved starspot crossings are indeed the root cause of the
correlation shown in Figure~\ref{fig:corr}.
While we do not have a solution to this contradiction, 
the injection-recovery tests discussed in
Section~\ref{subsec:ttvslope} provide some assurance that the
TTV-slope correlation is not simply a systematic artifact.

@@

The transit asymmetry seems robust against most methods of binning the
data, though with some caveats ({\it e.g.}, the ``middle quartile'' in
local flux, ${\rm d}f/{\rm d}t\in[3.0,32.5]\,{\rm ppt\,day}^{-1}$,
where the asymmetry does not appear).  Nonetheless, if the asymmetric were
systematic we might expect its parity to reverse as a function of
the sign of the local slope, and it does not.  We therefore entertained four
possible astrophysical explanations: gravity darkening, transit
timing variations, spot-crossing events, and a persistent asymmetric
dusty outflow.

@@

The scenario of transit timing variations (TTVs) producing the
asymmetry seems unlikely because the transit
timing variations we do observe are correlated with the local light
curve slope, which increases roughly as much as it decreases.  From
our analysis, the mean TTV and its standard deviation are
$0.66\pm5.53$ minutes; similarly the mean local slope and its
standard deviation are $0.59\pm45.50$\,ppt\,day$^{-1}$.  There is
therefore little expectation for TTVs to produce the asymmetry.  A
separate line of argument comes from Figure~\ref{fig:phaseslope}.  If
the local slope were essential to producing the transit asymmetry, we
would expect that in the largest ${\rm d}f/{\rm d}t$ bin, ${\rm
d}f/{\rm d}t\in[3.0,32.5]\,{\rm ppt\,day}^{-1}$, the sign of the
asymmetry would reverse.  We do not see evidence for this being the
case.

The third and related possibility is that of starspot crossings.
Young stars have higher spot-covering fractions than old stars ({\it
e.g.}, \citealt{morris_relationship_2020}).  Young solar-type stars
may also host dark starspots at high stellar latitudes \citep[{\it
e.g.}, EK~Dra;][]{strassmeier_starspots_2009}, though interferometric
imaging of spotted giant stars has shown different starspot latitude
distributions than those inferred from Doppler imaging
\citep{roettenbacher_contemporaneous_2017}.  Regardless, for any
spot-crossing anomalies to add coherently over the 140 Kepler
transits, it seems likely that we would need either for spots to be
persistent at a particular latitude (and for the planetary orbit to be
somewhat misaligned), or for a ``stroboscopic'' longitudinal phasing
\citep[{\it e.g.},][]{dai_stellar_2018}.  For our system, $P_{\rm
orb}/P_{\rm rot} \approx 2.76$, which means that every 4 transits and
11 stellar rotations, the planet crosses over roughly the same stellar
longitude, which might enable the necessary phasing if the spot-groups
are large and long-lived.  Unfortunately, the  S/N per Kepler transit
is $\approx8$, which renders individual spot-crossing events
unresolved.  This explanation seems marginally plausible, mainly
because the expected spot-crossing anomaly amplitudes ($\approx
100\,{\rm ppm}$) resemble the observed amplitude of the asymmetry
($\approx 50\,{\rm ppm}$).  One issue with this explanation however is
that there is no reason to expect starspot crossing events to last
exactly half the transit duration.
